%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Stephen George} & Email : \href{mailto:stephengeorge.work@gmail.com}{stephengeorge.work@gmail.com}\\
  \href{https://github.com/stephengeorge568}{Github} & Mobile : (402) 359-0543 \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Hudl}{Lincoln, NE}
      {Software Engineer II}{April 2024 - Present}
      \resumeItemListStart
        \resumeItem{Entity Relationship Microservice}
          {Architected and launched a .NET microservice managing entity relationships across Hudl's platform. Built an extensible foundation for any relationship type, now used by approximately a dozen products within Hudl.}
        \resumeItem{Custom Form Platform}
          {Designed and developed a .NET microservice with reusable React components and TypeScript logic for dynamic form creation, rendering, and completion across Hudl's products. Led development of a secure file upload and download feature with malware scanning, in-memory magic-byte file type verification, and layered infrastructure and application-level access controls. Created a plug-and-play solution with a generic, extensible architecture, starting with client data collection on Hudl's payments platform.}
        \resumeItem{Calendar Event Filter Project}
          {Owned development of a React-based tree filter panel enabling users to filter calendar events. Proactively identified early risks with tightly coupled UI components, then organized and led a multi-team decoupling effort, unblocking dependencies and ensuring successful, on-time delivery.}
        \resumeItem{AI Agent Orchestration \& Tooling}
          {Built an API automation orchestration system using Claude Code subagents with runtime feedback loops, enabling coding agents to autonomously author API test suites and reducing QA engineers' automation time by \~{}75\%. Drove broader AI tooling adoption by authoring internal guides and leading org-wide workshops, tracking success metrics and cost analysis to evaluate scalability for engineering team adoption.}
        \resumeItem{Production Operations Manager}
          {Managed production operations for 40+ engineers, organizing on-call rotations, preseason audits, and pushing for more efficient microservice resource allocation while responsibly balancing database connections, thread usage, AWS limitations, and more.}
      \resumeItemListEnd

    \resumeSubheading
      {Hudl}{Lincoln, NE}
      {Software Engineer I}{April 2023 - April 2024}
      \resumeItemListStart
        \resumeItem{iOS Video Upload Hotfix}
          {Delivered critical hotfix for iOS video upload issue affecting thousands of events by identifying a cross-version defect in Objective-C/Swift pipeline; implemented fix with enhanced observability for future detection.}
        \resumeItem{React Native Scoreboard Overlay}
          {Built React Native frontend feature to manage scoreboard overlay in livestream for sports events.}
      \resumeItemListEnd

    \resumeSubheading
      {Gallup}{Omaha, NE}
      {Software Engineer Intern}{May 2022 - August 2022}

    \resumeSubheading
      {Union Pacific}{Omaha, NE}
      {Software Development Intern}{September 2020 - November 2021}

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Monaco}
      {Built a real-time collaborative editor supporting multiple concurrent users using websockets. Initially developed with Java, Angular, Spring Boot, and Docker, then later translated to C\# and React. Implemented operational transformation algorithm for conflict resolution and synchronization at scale. \href{https://github.com/stephengeorge568/monaco}{GitHub Repository} 2022}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Nebraska - Omaha}{Omaha, NE}
      {Bachelor of Science in Computer Science; Minors: Cybersecurity \& Mathematics}{August 2019- Dec 2022}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Technologies}{: C\#, Typescript, React, AWS, Git CLI, Docker, Linux, Terraform, GraphQL, MongoDB, Java, Spring Boot}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
